### 2022-03-28 manuscript.tex
Update 02.tubaseq.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/c0eb8807f43cb1cfa23b023bee6fccf181e816ec.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/c0eb8807f43cb1cfa23b023bee6fccf181e816ec/checks
https://github.com/scherzerthesis/thesis/actions/runs/2053168894

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/811a8b3bb3b4ebbd000e6e5f7822e0778a33601f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/811a8b3bb3b4ebbd000e6e5f7822e0778a33601f}{scherzerthesis/thesis@811a8b3}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c0eb8807f43cb1cfa23b023bee6fccf181e816ec/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c0eb8807f43cb1cfa23b023bee6fccf181e816ec}{scherzerthesis/thesis@c0eb880}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.png}
\caption{\textbf{Figure 2.1. Overview of Tuba-Seq experimentation} (A) Lenti-sgRNA-Cre plasmid library with collection of targeted tumor supressors. \emph{Braf\textsuperscript{CAT/+}} and \emph{Braf\textsuperscript{CAT/+};H11b\textsuperscript{LSL-Cas9/+}} were infected with either 10\textsuperscript{4} (16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}}) or 10\textsuperscript{5} (8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} and 16 weeks \emph{Braf\textsuperscript{CAT/+}} alone) (B) text.}\label{fig:04}
}
\end{figure}
